Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-05 prop.tex
prop.tex \section{Real Interval-valued Frame Functions} Updating...

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
$\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.\end{lemma}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
\begin{eqnarray*}
\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq & \bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq & \bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
\end{eqnarray*}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

Moreover, the same argument can apply on the great circle which is
not longitude. Since $\ket{\bar{1}}$ is the normal vector of the
gray circle which includes $\ket{2}$ and $\ket{\bar{2}}$, we have
$\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
longitude, then $\bar{f}\left(\ket{\psi_{0}}\right)$ and $\bar{f}\left(\ket{\psi_{1}}\right)$
are still the same. Thus the lemma is proved.
\end{proof}
\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then $\theta_{0}>\frac{\pi}{4}$.\end{thm}
\begin{proof}
We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$,
we have $\left[\theta_{0},\frac{\pi}{2}\right]\cap\left[0,\frac{\pi}{2}-\theta_{0}\right]=\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\ne\emptyset$.
Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\right)$,
we have $\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$. Then, by lemma~\ref{lemma:imposs-imply-same-value},
for any $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
$\bar{f}\left(\ket{\psi_{1}}\right)=\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$.
In another word, $\bar{f}$ maps every state to $\imposs$, and cannot
be an interval-valued frame function.
\end{proof}

>>>>

\begin{lemma}\label{lemma:imposs-imply-same-value}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then there is $l_{0}\in\left[0,\frac{1}{2}\right]$ such that $\bar{f}\left(\ket{\psi_{0}}\right)=\left[l_{0},1-l_{0}\right]\in\mathscr{I}$
for any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$.\end{lemma}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-1} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-1}This figure is used in
the proof of lemma~\ref{lemma:imposs-imply-same-value}.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-1}.
Let the yellow circle is the states whose latitude is $\theta_{0}$.
Then, every states above the yellow circle maps to $\imposs$ by $\bar{f}$.
In particular, $\bar{f}\left(\ket{0}\right)=\bar{f}\left(\ket{0'}\right)=\imposs$.
Since $\left\{ \ket{0'},\ket{1},\ket{2'}\right\} $ is an orthonormal
basis, by lemma~\ref{lemma:interval-valued-frame-function}, we have
\begin{equation}
\begin{aligned}\left[1,1\right]-\bar{f}\left(\ket{1}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{2}\right)=\bar{f}\left(\ket{2'}\right)\\
\left[1,1\right]-\bar{f}\left(\ket{2'}\right) & \subseteq\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{1}\right)
\end{aligned}
\label{eq:includes}
\end{equation}
so that $\bar{f}\left(\ket{2'}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)$.
By the same reason, for any state~$\ket{\psi}$ in the dotted black
circle between $\ket{2'}$ and $\ket{2}$, we have $\bar{f}\left(\ket{\psi}\right)=\left[1,1\right]-\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)$.
Since the angle between $\ket{0}$ and $\ket{0'}$ is the same as
the angle between $\ket{2}$ and $\ket{2'}$, for any $\ket{\psi_{0}}$
and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are in the same longitude,
then $\bar{f}\left(\ket{\psi_{0}}\right)=\bar{f}\left(\ket{\psi_{1}}\right)$.

Moreover, the same argument can apply on the great circle which is
not longitude. Since $\ket{\bar{1}}$ is the normal vector of the
gray circle which includes $\ket{2}$ and $\ket{\bar{2}}$, we have
$\bar{f}\left(\ket{2}\right)=\left[1,1\right]-\bar{f}\left(\ket{\bar{1}}\right)=\bar{f}\left(\ket{\bar{2}}\right)$.
In another words, for any $\ket{\psi_{0}}$ and $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\theta_{0}\right]\right)$,
even if $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$ are not in the same
longitude, then $\bar{f}\left(\ket{\psi_{0}}\right)$ and $\bar{f}\left(\ket{\psi_{1}}\right)$
are still the same.

Thus, we could plug $\bar{f}\left(\ket{1}\right)=\bar{f}\left(\ket{2'}\right)=\left[l_{0},r_{0}\right]$
into equation~(\ref{eq:includes}), and get 
\begin{eqnarray*}
 &  & \left[1-r_{0},1-l_{0}\right]=\left[1,1\right]-\left[l_{0},r_{0}\right]=\left[l_{0},r_{0}\right]\\
 & \Rightarrow & l_{0}+r_{0}=1
\end{eqnarray*}
Also, we have 
\begin{eqnarray*}
 &  & 1\in\bar{f}\left(\ket{0'}\right)+\bar{f}\left(\ket{1}\right)+\bar{f}\left(\ket{2'}\right)=\left[2l_{0},2r_{0}\right]\\
 & \Rightarrow & l_{0}\le\frac{1}{2}\le r_{0}
\end{eqnarray*}
Thus the lemma is proved.
\end{proof}
\begin{thm}\label{thm:pi-div-4}Given $\theta_{0}\in\left[0,\frac{\pi}{2}\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then $\theta_{0}>\frac{\pi}{4}$.\end{thm}
\begin{proof}
We are going to prove by contradiction. Suppose $\theta_{0}\le\frac{\pi}{4}$,
we have $\left[\theta_{0},\frac{\pi}{2}\right]\cap\left[0,\frac{\pi}{2}-\theta_{0}\right]=\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\ne\emptyset$.
Pick any $\ket{\psi_{0}}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}-\theta_{0}\right]\right)$,
we have $\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$. Then, by lemma~\ref{lemma:imposs-imply-same-value},
for any $\ket{\psi_{1}}\in\angle^{-1}\left(\left[0,\frac{\pi}{2}-\theta_{0}\right]\right)$,
$\bar{f}\left(\ket{\psi_{1}}\right)=\bar{f}\left(\ket{\psi_{0}}\right)=\imposs$.
In another word, $\bar{f}$ maps every state to $\imposs$, and cannot
be an interval-valued frame function.
\end{proof}
\begin{thm}\label{thm:arcsin-one-over-sqrt-three}Given $\theta_{0}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$
and an interval-valued frame function~$\bar{f}:S^{2}\rightarrow\mathscr{I}$,
if $\bar{f}\left(\ket{\psi}\right)=\imposs$ for every $\ket{\psi}\in\angle^{-1}\left(\left[\theta_{0},\frac{\pi}{2}\right]\right)$,
then $\unknown\in\mathscr{I}$.\end{thm}
\begin{proof}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.38]{real-frame-2} 
\par\end{centering}
\caption{\label{fig:three-dimensional-real-frame-2}This figure is used in
the proof of theorem~\ref{thm:arcsin-one-over-sqrt-three}. The latitude
of the yellow circle is $\theta_{0}=\frac{\pi}{2}-\frac{\pi}{5}\in\left(\frac{\pi}{4},\frac{\pi}{2}-\arcsin\left(\frac{1}{\sqrt{3}}\right)\right]$,
and the latitude of the green circle is $\frac{\pi}{5}=\frac{\pi}{2}-\theta_{0}$.}
\end{figure}
We could illustrate the situation in figure~\ref{fig:three-dimensional-real-frame-2},
where the latitude of of the yellow circle is $\theta_{0}$ and the
latitude of of the green circle is $\frac{\pi}{2}-\theta_{0}$. Therefore,
$\bar{f}$ should map any state above the yellow circle to $\imposs$
and any states between the green circle and the equator to the same
interval, say, $\left[l_{0},1-l_{0}\right]$, where $0\le l_{0}\le\frac{1}{2}$. 
\end{proof}
